Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-01 aosd13/Evaluation.tex
Add better-named labels (ch:aosd13-...) to aosd13 chapters
Drop trailing whitespace everywhere
Done with
```
git grep -l ' \+$' '*.tex' '*.lhs'|xargs gsed -i'' -e 's/ \+$//'
```
Tune figure setup
Move figures to separate files before reordering

\newcommand{\graphPath}[1]{aosd13/graphs/#1}
\input{aosd13/graphs/evalRes}
\chapter{Evaluating SQuOpt}
\label{sec:evaluation}

@@

\begin{figure}
	\centering
		\includegraphics[width=\linewidth]{aosd13/graphs/measurements-overview}
	\caption{Measurement Setup: Overview}
	\label{fig:measurements-overview}
\end{figure}

@@

%Omit - this only showcases BAT, not our code. Show our implementation instead.
\begin{figure}
\centering
%\begin{lstlisting}
%for {
%  cf <- classFiles
%  m @ Method(_, "equals", MethodDescriptor(Seq(cf.thisClass), BooleanType), _) <- cf.methods 
%  if m.isAbstract
%} yield (cf, m)
%\end{lstlisting}
%import BATLifting._
\begin{lstlisting}
for {
  classFile <- classFiles.asSquopt
  method <- classFile.methods
  if method.isAbstract && method.name ==# "equals" &&
     method.descriptor.returnType ==# BooleanType
  parameterTypes <- Let(method.descriptor.parameterTypes)
  if parameterTypes.length ==# 1 && parameterTypes(0) ==# classFile.thisClass
} yield (classFile, method)
\end{lstlisting}
\caption{Find covariant \code{equals} methods.}
\label{fig:covariant-equals}
\end{figure}

@@

\begin{figure}
\centering
\begin{lstlisting}
val methodNameIdx: Exp[Map[String, Seq[(ClassFile, Method)]]] = (for {
  classFile <- classFiles.asSquopt
  method <- classFile.methods
} yield (classFile, method)).indexBy(entry => entry._2.name)
\end{lstlisting}
\caption{A simple index definition}
\label{fig:indexes}
\end{figure}

>>>>

\newcommand{\graphPath}[1]{aosd13/graphs/#1}
\input{aosd13/graphs/evalRes}
\chapter{Evaluating SQuOpt}
\label{sec:evaluation}
\label{ch:aosd13-evaluation}

@@

\begin{figure}[htb]
	\centering
		\includegraphics[width=\linewidth]{aosd13/graphs/measurements-overview}
	\caption{Measurement Setup: Overview}
	\label{fig:measurements-overview}
\end{figure}

@@

\input{aosd13/fig-covariant-equals}

@@

\input{aosd13/fig-indexes}
